\chapter{Introduction}
\label{ch:intro}

This project investigates three fields in technology and their combined intersection.
It considers the role of trust in software systems, the promise of secure remote voting and the blossoming field of \gls{dlt} --- a.k.a. Blockchain Technology.

Trust in technology is becoming more relevant in a world where security breaches and data leaks make it into the general media. The public is more aware than ever that their use of technology comes with the potential for their information to be used in ways they did not intend. They make a decision ---consciously or not--- to trust the service provider in order to acquire the benefits of their service. For some, those who give it serious consideration, the decision will be made by weighing the benefit of using the service, the sensitivity of the data they give to the service against the trust they have in both the technology powering the service and the reputation of the service provider. Others may only consider the benefits and give the trust freely. The author believes that the former group, while in the minority now, will only grow as technology continues to advance and increasingly permeate our lives.

Voting is the core of the democratic process. The promise of remote voting, is the ease in which the electorate can perform this process, combined with the reduced cost for the organizing authorities of providing such a service remotely. Remote voting, provided it is at least as trustworthy as in person voting, appears to provide many benefits with few downsides. The potential benefits of convenience, cost, reliability and non-repudiation seem for far outweigh the potential downsides of requiring voters have access to the technology to participate --- a downside that exists in an analogous form for in-person voting in that voters are required to be able to visit a voting booth in a timely manner. Despite these potential benefits, very few large scale remote voting systems are in use.

\Gls{dlt} is a technology which at its core provides a distributed, immutable ledger that mutually distrusting parties can agree on. The surge of popularity in the last few years of cryptocurrencies ---such as Bitcoin, Ethereum and Zcash--- backed by \gls{dlt} has lead to much real-word testing of the reliability and practicality of various forms of the technology. Although the long-term future of cryptocurrencies is still to be seen, the technology itself has more than one use. One particular usage of note is its ability to create audit trails in which a single entity may add to the chain and many others ---possibly even the general public--- can validate the data to ensure consistency. As the data are shared as created, all entities with read access will be able to detect attempts at mutation. \Gls{dlt} however suffers its own popularity with the ``\emph{when all you have is a hammer, everything looks like a nail}'' issue of a solution in search of a problem. ``\emph{Blockchain}'' has become a technology buzzword and many projects are emerging that use \gls{dlt} in places where it is simply unnecessary and an over-complication. We will need a convincing argument that the use of \gls{dlt} is bringing benefit rather than simply a being a solution in need of a problem.

Taking these fields together, can we utilize the \gls{dlt} to help provide a remote voting system with low trust requirements? This report will investigate the process of remote voting, looking at various systems proposed and implemented to see how they address the issues of trust. It will describe \gls{dlt} and its various usages and properties to see how it might be best used in the context of remote voting systems. Indeed, we should be able to show that using \gls{dlt} in such a system actively provides benefit. With this information, we will be in a position to propose and implement a remote voting system which uses the best of this knowledge to provide a voting platform with minimal trust requirements.


\section{Motivation}
\label{ch:intro:motiv}

The author is a software engineer and very interested in both cryptography and the role of trust in software systems. Trust in the democratic process and hence election systems is also of great importance, as evidenced by the amount of contestation around the results of the 2020 US presidential elections. There has been a large amount of prior research into voting systems \cite{
    panjaSecureEndtoendVerifiable2018,
    mccorrySmartContractBoardroom2017,
    liuEvotingProtocolBased2017,
    yangBlockchainVotingPublicly2020,
    spadaforaCoercionResistantBlockchainBasedEVoting2020,
    dimtiriouEfficientCoercionfreeUniversally2019,
    tsoukalasHeliosZeus2013,
    xiaVersatilePretVoter2010,
    ryanPrEtVoterVoterVerifiable2010,
    yuPlatformindependentSecureBlockchainBased2018,
    seifelnasrScalableOpenVoteNetwork2020,
    gajekTrustlessCensorshipResilientScalable2019,
    chillottiHomomorphicLWEBased} and properties of voting systems yet very few national level deployments exist. Could a lack of trust in the technology be the reason for the low adoption? Or are there more fundamental technical or societal reasons that these systems are not in place. It seems that a voting system with \emph{universal verifiability} (see \autoref{ch:req:sec}) would make any contestation to the outcome provably valid or invalid.

The trust aspect seems especially relevant. How many entities must we trust? How many must be honest before the system falls down? What are the probabilities of an adversary being able to manipulate the voters, the votes or the tally? Although the average voter may not ask themselves these exact questions, they will likely make an intuition-based judgement on how much they trust the voting process. Whether this lack of trust in the system will lead them to protest, abstain, or simply accept and continue is another question, but not one technology can answer. However, the author would speculate that for an electronic voting system to be acceptable for an electorate its trustworthiness must be sufficiently high and reducing trust requirements works towards that goal.

Therefore, this report is an opportunity to investigate the trust requirements in various electronic voting systems and how those requirements might be minimized.


\section{Objectives}
\label{ch:intro:object}

This report aims to:

\begin{enumerate}
    \item Describe the security properties desirable in e-voting schemes.
    \item Analyse existing e-voting schemes, their security properties and identify areas that require significant trust from the user.
    \item Introduce the technologies and cryptographic systems we can leverage to design a better system.
    \item Propose and provide a software implementation of a scheme that is minimizes trust requirements while maximizing coverage of the desirable security properties.
    \item Analyse the protocol and the success of the implementation against the objectives set out for it.
    \item Form a conclusion whether we {\textbf{can}} reach a minimum level of trust requirement while maintaining the desirable security properties.
\end{enumerate}


\section{Structure of the Report and Methodology}
\label{ch:intro:method}

The compilation of this report was done in a number of stages. The first was a literature review to ascertain the status quo. As mentioned, there is a lot of work published regarding voting systems and the first step was to find relevant material to get a picture of the current state of the art. The literature review also surfaced the common vocabulary for discussing the security properties of voting and e-voting systems and highlighted the common threads in the different technologies used.

The second stage was to take all the data from the literature and evaluate the different systems with respect to the security properties and also with respect to the trust requirements they imposed on their users. A variety of schemes were chosen to provide a broad view of the different approaches to the same problems.
% In this stage Helios was chosen as for deeper analysis in the most part due to its maturity, real-world use and open source codebase.
This stage led to an understanding of the core of electronic voting systems, how the security properties relate to trust and how the technologies involved, despite being different in methodology and efficacy, all operate towards similar goals.

The third stage was to build a picture for how a system with minimal trust requirements might be constructed. This stage introduced the cryptographic primitives that would be useful and the exploration blockchain technology as a tool for operating with transparency to reduce trust requirements. Once the system had shape, a software implementation of the system was created to demonstrate its feasibility. The process of creating a software implementation in turn provided feedback into the design and the final proposal and implementation where created concurrently.

The fourth stage was to analyse the success of the protocol, given the aims of providing desired security properties whilst minimizing trust requirements in a practical solution that could scale up to state-level elections. The conclusion then covers the main objectives of the report in light of the analysis, proposal, and success of implementation.

The report is intended to be read in order, and as such introduces concepts as needed. It covers the principles behind the voting systems, moves on to the technologies, introduces \gls{dlt} and finally moves on to the proposal of a voting system.

\begin{itemize}
    \item \textbf{Introduction:} This section (\autoref{ch:intro}) introduces the concepts, methodology and motivation for the report.
    \item \textbf{Voting Systems:} The systems, their security properties and trust requirements
          %and the further analysis of the Helios protocol
          are covered by \autoref{ch:req} and \autoref{ch:ev}. % and \autoref{ch:helios}.
    \item \textbf{Distributed Ledger Technology:} Blockchain technology and its applications in voting systems is covered by \autoref{ch:blockchain}.
    \item \textbf{Proposal:} A proposal for a voting system, its implementation and the analysis are covered by \autoref{ch:astris}, \autoref{ch:sw} and \autoref{ch:analysis}.
    \item \textbf{Conclusion:} The concise summary of findings is performed in \autoref{ch:conclusion}.
\end{itemize}




