\chapter{Data types in the Astris Protocol}
\label{appendix:datatypes}

This is a list of the data types used for the block payloads in the Astris system. Some nested structures are broken out to minimize repetition.

All strings in this specification are defined as UTF-8 encoded text, including numeric representations.

Note that in all the serialized representations, integers marked as \texttt{BigInt} are arbitrary size and there will be serialized to strings as the base64url (\rfc{4648}) encoding with padding characters stripped. The integers should be treated as unsigned and converted to big-endian bytes before the encoding takes place.

We also list the construction of the signature messages where appropriate, but the full construction of a signature is defined with the \dtref{Signature}{dt:elgamal:pok} data type.

\section*{Payload hints: \texttt{kind}}
\label{dt:payload:hints}
\begin{lstlisting}[style=ES6]
    1 = PayloadElectionSetup
    2 = PayloadTrusteeShares
    3 = PayloadTrusteePublic
    4 = PayloadVoterRegistration
    5 = PayloadVoteCast
    6 = PayloadPartialTally
\end{lstlisting}

\section*{\texttt{PayloadElectionSetup}}

\label{dt:payload:setup}
\begin{lstlisting}[style=ES6]
// PayloadElectionSetup: kind=1
{
    protcolVersion:         "1.0"
    name:                   string
    blockDifficulty:        integer
    encryptionSharedParams: ElGamalParameters
    trusteesRequired:       integer
    candidates:             Array<string>
    maxChoices:             integer
    trustees:               Array<TrusteeSetup>
    registrar:              RegistrarSetup
    timing:                 TimingInfo
}
\end{lstlisting}
\vspace*{-0.95em}
\label{dt:elgamal:params}
\begin{lstlisting}[style=ES6, firstnumber=last]
// ElGamalParameters
{
    p: BigInt // The group prime,
    q: BigInt // The sub-group prime,
    g: BigInt // The generator for the group
}
\end{lstlisting}
% this needs a page break.
\newpage
\label{dt:trustee}
\begin{lstlisting}[style=ES6, firstnumber=last]
// TrusteeSetup
{
    name:               string
    verificationKey:    PublicKey
    encryptionKey:      PublicKey
    encryptionProof:    ProofOfKnowledge
    publicExponents:    Array<BigInt>    // length = trusteesRequired + 1
    signature:          Signature
}
\end{lstlisting}
\vspace*{-0.95em}
\label{dt:registrar}
\begin{lstlisting}[style=ES6, firstnumber=last]
// RegistrarSetup
{
    name:               string
    verificationKey:    PublicKey
    registrationURL:    string
    signature:          Signature
}
\end{lstlisting}
\vspace*{-0.95em}
\label{dt:timing}
\begin{lstlisting}[style=ES6, firstnumber=last]
// TimingInfo
{
    timeZone:               string      // IANA timezone specifier
    parameterConfirmation:  TimeBounds
    voterRegistration:      TimeBounds
    voteCasting:            TimeBounds
    tallyDecryption:        TimeBounds
}
// TimeBounds
{
    opens:  string // ISO8601 Timestamp with second precision
    closes: string // and no timezone information. e.g. `2020-01-13T18:00:00`
}
\end{lstlisting}

The signature for a \texttt{TrusteeSetup} is calculated with using a message created by concatenation of:
\begin{enumerate}
    \item the literal string \lstinline[style=ES6]{"trustee:"}
    \item the base10 representation of the trustee index (0-based)
    \item the literal string \lstinline[style=ES6]{":"}
    \item the base16 (lowercased) representation of the encryption public key \texttt{Y} value
    \item for each \texttt{publicExponent}:
          \begin{enumerate}
              \item the literal string \lstinline[style=ES6]{":"}
              \item the base16 (lowercased) representation of the exponent
          \end{enumerate}
\end{enumerate}

The signature for a \texttt{RegistrarSetup} is calculated with using a message created by concatenation of:

\begin{enumerate}
    \item the literal string \lstinline[style=ES6]{"registrar:"}
    \item the \texttt{registrationURL}
\end{enumerate}

\newpage % or just the title will be on one page.
\section*{\texttt{PayloadTrusteeShares}}
\label{dt:payload:shares}
\begin{lstlisting}[style=ES6]
// PayloadTrusteeShares
{
    trusteeIndex:   integer
    shares:         Array<EncryptedShare> // length = number of trustees - 1
}
\end{lstlisting}
\vspace*{-0.95em}
\label{dt:encshare}
\begin{lstlisting}[style=ES6, firstnumber=last]
// EncryptedShare
{
    recipient:  integer     // the trusteeIndex this is for
    point:      CipherText  // encrypted with recipient public encryption key
    signature:  Signature
}
\end{lstlisting}

The trustee shares for a trustee with index $i$ out of $N$ trustees should be an array of encrypted shares for each $j$ where $j \neq i$ and $0 <= j <= N$. The signature on an encrypted share is constructed by the concatenation of:

\begin{enumerate}
    \item the literal string \lstinline[style=ES6]{"share:"}
    \item the base10 representation of the trustee index $i$
    \item the literal string \lstinline[style=ES6]{":"}
    \item the base10 representation of the recipient trustee index $j$
    \item the literal string \lstinline[style=ES6]{":"}
    \item the base10 representation of the trustee index $i$
    \item the literal string \lstinline[style=ES6]{":"}
    \item the base16 (lowercased) representation of the point ciphertext \texttt{a} value
    \item the literal string \lstinline[style=ES6]{":"}
    \item the base16 (lowercased) representation of the point ciphertext \texttt{b} value
\end{enumerate}

\section*{\texttt{PayloadTrusteePublic}}
\label{dt:payload:public}
\begin{lstlisting}[style=ES6]
// PayloadTrusteePublic
{
    trusteeIndex:   integer
    shardKey:       PublicKey
    shardProof:     ProofOfKnowledge // of the PrivateKey paired to "shardKey"
    signature:      Signature
}
\end{lstlisting}

The signature on the trustee public data is constructed by the concatenation of:

\begin{enumerate}
    \item the literal string \lstinline[style=ES6]{"shard:"}
    \item the base10 representation of the trustee index (0-based)
    \item the literal string \lstinline[style=ES6]{":"}
    \item the base16 (lowercased) representation of the \texttt{shardKey} public key \texttt{Y} value
\end{enumerate}

\section*{\texttt{PayloadVoterRegistration}}
\label{dt:payload:reg}
\begin{lstlisting}[style=ES6]
// PayloadVoterRegistration
{
    voterId             string    // only the registrar knows the mapping between voterId and voter
    verificationKey:    PublicKey // voters own verificationPublic key
    registrarSig:       Signature // signed with the registrar's signing key
    voterSig:           Signature // signed with the voters signing key
}
\end{lstlisting}

The signature \texttt{registrarSig} on the voter registration object is produced by the Registrar. The message is constructed by concatenation of:

\begin{enumerate}
    \item the literal string \lstinline[style=ES6]{"voter:r:"}
    \item the base16 (lowercased) representation of the SHA256 sum over the \texttt{voterId}.
    \item the literal string \lstinline[style=ES6]{":"}
    \item the base16 (lowercased) representation of the \texttt{verificationKey} public key \texttt{y} value
\end{enumerate}

The signature \texttt{voterSig} on the voter registration object is produced by the Voter, using the private key associated with the \texttt{verificationKey} in the object. The message is constructed by concatenation of:

\begin{enumerate}
    \item the literal string \lstinline[style=ES6]{"voter:v:"}
    \item the base16 (lowercased) representation of the SHA256 sum over the \texttt{voterId}.
    \item the literal string \lstinline[style=ES6]{":"}
    \item the base16 (lowercased) representation of the \texttt{registrarSig} \texttt{r} value
\end{enumerate}

\section*{\texttt{PayloadVoteCast}}
\label{dt:payload:cast}
\begin{lstlisting}[style=ES6]
// PayloadVoteCast
{
    voterId:    string
    votes:      Array<BigInt>                      // length = number of candidates
    proofs:     Array<ZeroKnowledgeProofOneOrZero> // length = number of candidates
    proof:      ZeroKnowledgeProofOneOfX
    signature:  Signature
}
\end{lstlisting}

The \texttt{proofs} array contains \glsplural{zkp} for each vote, to prove that the encrypted vote is either a $0$ or $1$.

The \texttt{proof} gls{zkp} is a proof that the sum of ciphertexts contains a number between $0$ and the configured \texttt{maxChoices} from the \texttt{PayloadElectionSetup}.

The signature is created with the voter's private key and the message is constructed by concatenation of:

\begin{enumerate}
    \item the literal string \lstinline[style=ES6]{"ballot:"}
    \item the base16 (lowercased) representation of the SHA256 sum over the \texttt{voterId}.
    \item for each element of \texttt{votes}
          \begin{enumerate}
              \item the literal string \lstinline[style=ES6]{":"}
              \item the base16 (lowercased) representation of the value
          \end{enumerate}
\end{enumerate}

\section*{\texttt{PayloadPartialTally}}
\label{dt:payload:tally}
\begin{lstlisting}[style=ES6]
// PayloadPartialTally
{
    trusteeIndex:   integer
    tallies:        Array<CipherText>           // in candidate order
    decrypted:      Array<BigInt>               // in candidate order
    proofs:         Array<ZeroKnowledgeProof>   // in candidate order
    signature:      Signature
}
\end{lstlisting}

The \texttt{proofs} array contains \glsplural{zkp} for each decryption, proving the correct partial application of the shard key of the trustee.

The signature is created with the trustee's private signing key and the message is constructed by concatenation of:

\begin{enumerate}
    \item the literal string \lstinline[style=ES6]{"tally:"}
    \item the base10 representation of the trustee index
    \item for each ciphertext of \texttt{tallies}
          \begin{enumerate}
              \item the literal string \lstinline[style=ES6]{":"}
              \item the base16 (lowercased) representation of the \texttt{a} value
              \item the literal string \lstinline[style=ES6]{":"}
              \item the base16 (lowercased) representation of the \texttt{b} value
          \end{enumerate}
    \item for each element of \texttt{decrypted}
          \begin{enumerate}
              \item the literal string \lstinline[style=ES6]{":"}
              \item the base16 (lowercased) representation of the value
          \end{enumerate}
\end{enumerate}

\section*{Common Structures}

\label{dt:elgamal:pk}
\begin{lstlisting}[style=ES6]
// PublicKey
{ y: BigInt }
\end{lstlisting}
\vspace*{-0.95em}
\label{dt:elgamal:sk}
\begin{lstlisting}[style=ES6, firstnumber=last]
// SecretKey
{ x: BigInt }
\end{lstlisting}
%\vspace*{-0.95em}
\newpage %
\label{dt:elgamal:keypair}
\begin{lstlisting}[style=ES6, firstnumber=last]
// KeyPair
{
    pk: PublicKey
    sk: SecretKey
}
\end{lstlisting}
\vspace*{-0.95em}
\label{dt:elgamal:ct}
\begin{lstlisting}[style=ES6, firstnumber=last]
// CipherText
{
    a: BigInt // known as "alpha"
    b: BigInt // known as "beta"
}
\end{lstlisting}
\vspace*{-0.95em}
\label{dt:elgamal:pok}
\begin{lstlisting}[style=ES6, firstnumber=last]
// ProofOfKnowledge (of a SecretKey) / Signature (over a defined message)
// Both constructs share the same properties
{
    c: BigInt
    r: BigInt
}
\end{lstlisting}
\vspace*{-0.95em}
\label{dt:elgamal:zkp}
\begin{lstlisting}[style=ES6, firstnumber=last]
// ZeroKnowledgeProof
{
    a: BigInt,
    b: BigInt,
    c: BigInt,
    r: BigInt,
}
// ZeroKnowledgeProofOneOrZero
// represented as a tuple of 2 proofs
[ZeroKnowledgeProof, ZeroKnowledgeProof]

// ZeroKnowledgeProofOneOfX
// represented as an X-tuple of proofs,
[ZeroKnowledgeProof, ..., ZeroKnowledgeProof] // length = X
\end{lstlisting}


\chapter{Common Processes in the Astris Protocol}
\label{appendix:processes}

We note here that many cryptographic operations assume a random oracle. That is a function that given a sequence of bytes, produces a deterministic second sequence of bytes where there is no discernable relation between the two sequences. Cryptographic Hash functions fulfil this property with high confidence and therefore when a random oracle is required, we instead use a hash function. For Astris \texttt{1.0} the hash function used for all random oracle substitution is the SHA256 digest function.


\section*{Signature}
\label{proc:sign}

Astris uses Schnorr signatures described fully in \rfc{8235}. We start with our system parameters $p$, $q$ and $g$, the secret key $a$ (with public key  $A = g^a\ \textrm{mod}\ p$) and a random number $v \in_R \mathbb{Z}_q$. We then calculate $V = g^v\ \textrm{mod}\ p$. Now we create the message to be signed in a manner specific to the data we wish to sign, each data type with a signature has the details of how their message should be constructed. Assume that message is created as an array of bytes: $m$.

Now we create the commitment $c = H(V || A || m)\ \textrm{mod}\ q$ where $H$ is the SHA256 hash function and the concatenation is done as follows:

\begin{enumerate}
    \item Start with the string (UTF8 encoded): \lstinline[style=ES6]{"sig|"}.
    \item Then append the base16 (lowercased) representation of $V$.
    \item Append a pipe character \lstinline[style=ES6]{"|"}.
    \item Then append the base16 (lowercased) representation of $A$.
    \item Append a pipe character \lstinline[style=ES6]{"|"}.
    \item Then append the raw bytes of the message $m$.
\end{enumerate}

Now we calculate the response $r = v - ac\ \textrm{mod}\ q$. The signature is now the pair $(c, r)$.

To verify the signature we recreate $V = g^r * A^c\ \textrm{mod}\ p$, and therefore the expected challenge message $C = H(V || A || m)\ \textrm{mod}\ q$ in the same way as during creation. Then we check:

\begin{enumerate}
    \item $A$ is a valid public key for this system
    \item $C \equiv c$ the challenge we created is the same as the given one.
\end{enumerate}

\section*{Proof Of Knowledge of Secret Key}
\label{proc:pok}

The Proof of Knowledge construct is a \gls{zkp}. In fact, it is exactly the same construct as the Signature. Consider that to create a valid signature, one must possess the secret key, so \emph{any} signature that is valid by definition proves the possession of the private key. So we perform the exact same process as the defined for Signature, with the fixed message of \lstinline[style=ES6]{"pok"}.

\section*{Zero Knowledge Proofs}
\label{proc:zkp}

We have two \glsplural{zkp} that both rely on the same core process. We will describe it once and then describe the two distinct processes. The general method is specified in \cite{camenischProofSystemsGeneral}.

Firstly, we have the system parameters $(g,p,q)$ and choose a random $w \in \mathbb{Z}_q$. Let us consider the following parameters we choose: $h \in \mathbb{Z}_p$ is public knowledge and $s \in \mathbb{Z}_q$ is the secret knowledge we wish to prove we know, but not reveal. Let $G = g^s$ and $H = h^s$ be public. Finally, we have a function $F$ which produces a challenge $C \in \mathbb{Z}_q$ in a random oracle model. The exact specifics depend on the type of proof.

The prover calculates:

\begin{enumerate}
    \item Commitment A: $t_1 = g^w$
    \item Commitment B: $t_2 = h^w$
    \item A challenge with: from $C = F()$, $F$ may use any public parameters known so far.
    \item A Response $R = (w - sC)\ \textrm{mod}\ q$
\end{enumerate}

The proof is the tuple $(t_1, t_2, C, R, G, H)$.

The verifier can now take the public information $(g,p,q,h)$ and the proof $(t)_1, t_2, C, R, G, H)$ and check:

\begin{enumerate}
    \item $g^R mod p = (t_1G^C)\ \textrm{mod}\ p$
    \item $h^R mod p = (t_2H^C)\ \textrm{mod}\ p$
    \item That the challenge $C$ was created correctly from the data, which will be specific to the type of proof.
\end{enumerate}

\subsection*{Zero Knowledge Proof of Correct Decryption}
\label{proc:zkp:dec}

As we are using ElGamal over a finite field for encryption, we can prove that a plaintext comes from a ciphertext without revealing our secret key. Let us remember the encryption and decryption functions over the parameters $(p,q,g)$.

To encrypt a message $m$ with a public key $y$ we need randomness $r \in_{R} \mathbb{Z}_q$. Then we calculate $a = g^r\ \textrm{mod}\ p$ and $b = mh^r\ \textrm{mod}\ p$. The ciphertext is $(a,b)$

To decrypt the ciphertext $(a,b)$ with private key $x$ we calculate $m = ba^{-x}\ \textrm{mod}\ p$.

The decryption function can be rearranged as $b/m = a^x$ and the public key is $y = g^x$. So we can create a \gls{zkp} with a simple challenge function over $(t_1, t_2)$ that we have defined using our random oracle function over the message created by concatenation of:

\begin{enumerate}
    \item the literal string \lstinline[style=ES6]{"zkp:dec|"}
    \item the base16 (lowercased) representation of $t_1$
    \item the literal string \lstinline[style=ES6]{"|"}
    \item the base16 (lowercased) representation of $t_2$
\end{enumerate}

The public parameters are $s = x$, $g = g$, $G = g^s = g^x = y$, $h = a$, $H = a^s = a^x = b/m$ (we have the ciphertext and plaintext as we have decrypted the value).


\subsection*{Zero Knowledge Proof of Encryption of One of a Set of Plaintexts}
\label{proc:zkp:enc}

This one is more complex. We wish to prove that the ciphertext given is a valid encryption of one of a set of possible plaintexts. The possible texts are public.

In this situation we use the method for create a proof that we know one piece of knowledge from a group described in \cite{camenischProofSystemsGeneral} to create a set of proofs over the possible plaintexts, where all but the \emph{real} values are faked. We use the fake commitments from the fake proofs, along with the real commitment, to create an overall challenge value. We then subtract the fake challenge values from the overall challenge value to create the challenge for the real proof.

In this situation, the verifier cannot tell which proof is the real one, but can check that they all verify. They can also sum the challenge values and check that they match the calculated challenge value for a commitment over all the proofs. If so, then the plaintext must indeed be one of the given values.

The prover has the list of plaintexts $(m_1, m_2, ..., m_k)$, the ciphertext $(a,b)$ and the randomness $r$ used in the encryption. There is also a publicly known piece of metadata $d$ (in our case a hash of the voter's ID in the system) to prevent re-use of the \gls{zkp} in a separate context.

For each plaintext in the list where $i$ is the index:

If the plaintext $m_i$ \emph{isn't} the one encrypted, we create a fake proof. The fake proof calculates $b_i = b / m_i$ and two random values for the challenge and response $C \in_{R} \mathbb{Z}_q$ and $R \in_{R} \mathbb{Z}_q$. They then calculates the values for $(t_1, t_2)$ (which is done the other way around in a real proof). $t_1 = g^Ra^{-C}$ and $t_2 = y^Rb_{i}^{-C}$.

If the plaintext $m_i$ \emph{is} the actual one encrypted, we create a real proof with \gls{zkp} parameters $s = r$, $h = y$, $g = g$. This implies that $G = g^r = a$ and $H = h^r = y^r = (g^x)^r = (g^r)^x = a^x = b/m_i$. As all of these values are known we can construct the \gls{zkp} commitments $(t_1, t_2)$. To create the challenge for the real proof we combine \emph{all} the commitments for all fake and real proofs in order by using the random oracle over a message constructed by concatenation of:

\begin{enumerate}
    \item the literal string \lstinline[style=ES6]{"zkp:enc|"}
    \item for each proof in order:
          \begin{enumerate}
              \item the base16 (lowercased) representation of $t_1$
              \item the literal string \lstinline[style=ES6]{"|"}
              \item the base16 (lowercased) representation of $t_2$
              \item the literal string \lstinline[style=ES6]{"|"}
          \end{enumerate}
    \item the extra metadata passed in $d$ as raw bytes
\end{enumerate}

The final challenge value is the random oracle's response, minus each of the other proof's challenge values. This ensures the sum of the challenges is the overall challenge value.

The proof is then the list of tuples $(t_1, t_2, C, R)_1, (t_1, t_2, C, R)_2, ..., (t_1, t_2, C, R)_k$.

The verifier must verify the list of proofs, against the list of plaintexts, without doing the challenge check, but instead creating a sum of the challenges. Then the verifier should re-create the challenge using all the commitments in order and the known metadata $d$. The sum of the individual challenges should match the overall re-created challenge value.

\section*{Canonical JSON Encoding}
\label{proc:json}

In order to use JSON serialization as a precursor to hashing to generate the block hashes, we need to ensure that all clients will encode the data in exactly the same way. As such we define a canonical JSON encoding which is used to serialize objects into for hashing and storage on the chain. JSON is not a unique representation of any object, but we can make it so by tightening some loose constraints.

Whilst not directly related to canonical JSON, the \emph{big} integers in this spec ---for example those describing numbers in ciphertexts, signatures and keys--- are not serialized as raw integers despite the JSON spec allowing it. As most JSON decoding implementations would likely not accept these number, we prefer a string representation. This is described in the preamble of \autoref{appendix:datatypes}.

In order to create a \emph{canonical} encoding of an object the following tweaks to the standard are made:

\begin{enumerate}
    \item Objects will have their keys sorted lexically.
    \item Insignificant whitespace will be removed, i.e. no spacing or indentation
    \item No spurious Unicode replacements in strings ---i.e. `\texttt{<}' $\leftarrow$ `\texttt{\ue{003c}}'--- \textbf{except} for the \texttt{LINE SEPARATOR U+2028} and \texttt{PARAGRAPH SEPARATOR U+2029} which should be encoded as \texttt{\ue{2028}} and \texttt{\ue{2029}} respectively.
    \item After the encoding, we add a single line feed character, \texttt{ASCII 0x0A}, as a convenience for viewing the data manually.
\end{enumerate}

For a simple example, the object:

\newpage
\begin{lstlisting}[style=ES6]
{   "k": "<v/>",
    "a": { "b": 1,
            "a": 2 },
    "0": ["c",
          "b",
          "a"
] }
\end{lstlisting}

Would have the canonical representation (note the trailing newline):

\begin{lstlisting}[style=ES6,escapechar=\%]
{"0":["c","b","a"],"a":{"a":2,"b":1},"k":"<v/>"}
%
\end{lstlisting}

For reference, the SHA256 hash of the Canonical JSON encoding of that object include the trailing new line character, encoded as hex is:

\begin{lstlisting}[style=ES6]
"5a5f0c64d0dd15c9ed2e2baa994c36dac4ba55c5a64ffde7e984b35ff004a543"
\end{lstlisting}

\chapter{Astris gRPC Service Definition}
\label{appendix:grpc}

Astris gRPC specification, although part of the source code at {\surl{\astrisrepo}}, is useful to include.

\lstinputlisting[language=protobuf3, style=protobuf]{astris.proto}

Some points to note in the specification.

\begin{enumerate}
    \item \texttt{FromBlock} allows traversal from a block towards the end of the chain. The blocks themselves only have the hash of the previous block in them so iterating forward is more complex than iterating backwards. This method implies that implementations must be able to iterate over the chain in either direction.
    \item \texttt{AtDepth} allows a node to check the block ID that another node has at a specific depth in the chain allowing efficient calculation of where the two chains might diverge.
\end{enumerate}

\chapter{The Astris Blockchain}
\label{appendix:blockchain}

The Astris Blockchain implementation is fairly simple. Each block's payload is an arbitrary set of bytes. These encode various data structures, but to the chain they are just bytes. The block header contains all the other metadata which can be used to validate the block. Let us use the gRPC Protocol Buffer message definition as that is the externally visible definition.

\begin{lstlisting}[language=protobuf3, style=protobuf]
message BlockHeader {
    bytes   prev_id = 1;      // SHA256 hash of previous block
    bytes   payload_hash = 2; // SHA256 hash of the payload
    fixed32 timestamp = 3;    // unix timestamp of block creation
    fixed32 proof = 4;        // proof of work
    uint64  depth = 5;        // block height or chain depth
    uint32  kind = 6;         // type hint for the payload
}
\end{lstlisting}


The chain is maintained via \texttt{prev\_id} which is the previous block's ID, except for the genesis block which has all $0$ bytes here. The \texttt{payload\_hash} is a convenience, so we don't need to hash the entire payload each time we want to check the block ID. The \texttt{timestamp} is a 32bit unsigned integer representing seconds since the Unix epoch (00:00:00 on the 1st January 1970). The \texttt{depth} field is 64bit unsigned integer representing the block depth of this block in the chain, again a convenience to assist with validation and ordering. The \texttt{proof} field is a 32bit unsigned integer which is the result of our proof-of-work scheme explained later. Finally, we have the \texttt{kind} field which holds a hint as to the type of payload in this block. This is purely a convenience for the decoder to know in advance which data structure ought to be contained in the payload.

The block ID is defined as the SHA256 hash of the concatenation of the previous block ID, the payload hash, the timestamp, the proof and the kind hint. The previous block ID and payload hash are bytes already, but the timestamp, proof and kind are 32bit unsigned integers and must be converted to bytes using big-endian encoding. Note that the depth is in the block ID --- it is just metadata that could be calculated externally and attempts to place fake data in this field will be noticed swiftly so its integrity as part of the ID is superfluous.

In order to provide the proof of work, we define that the block ID must have $n$ leading 0 bits. That is, when considered as a number it should be less than the \emph{target} number. This is very straightforward to verify, but requires performing (on average) $2^n$ hashes before a valid value for the proof is found. The number of leading 0-bits is known as the \emph{difficulty} and is defined as $32$ for the genesis block ---which is less susceptible to post-facto forgery as the block ID is published as the election identifier--- and for every subsequent block by the value in the election setup data --- i.e. it is under control of the election authority.

Implementations should always consider the deepest valid chain as the correct one, however we should take careful note when a large change takes place as it may indicate adversarial behaviour. As such implementations are encouraged to keep all valid chains in storage, only considering the longest as true. The chains will make up a directed acyclic graph of blocks, with a single genesis and one longest branch. If more than one branch is equal longest, the implementation should pick the earliest final block as the true chain, but wait for new blocks to confirm which branch should be taken.